Forecasting biodiversity in breeding birds using best practices

### 2017-12-08 manuscript/reviewer_reply.Rmd

*Line 180 – Maybe also mention this is in the forecast package – as you do with gbm below?*

>We have added this.

*Line 183: Because these defaults may change over time, it’d be good to specify things like the ranges of AR / MA order that you searched over, which criteria was used to compare models, etc. And whether or not you included a drift parameter?*

>We agree that software can evolve over time and make methods non-repricable. We have add details of the auto.arima model in the suppliment.

### 2017-12-08 manuscript/draft.Rmd
reviewer answer and suppliment comment

![**A.** Model predictions for Pennsylvania route 35 when all observers are
treated the same (black points). **B.** Model predictions for the same route
when accounting for systematic differences between observers (represented by the
points' colors). In this example most models are made more robust to observer
turnover. Note that the "naive" model is less sensitive to observer turnover,
and does not benefit as much from modeling
it.](../figures/observer_predictions.png)

@@

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in the package `forecast`; @forecast1] to represent an array of
different time-series modeling approaches. These models can include an
autoregressive component (as in the "naive" model, but with the possibility of
longer-term dependencies in the underlying process), a moving average component
(where the noise can have serial autocorrelation) and an
integration/differencing component (so that the analysis could be performed on
sequential differences of the raw data, accommodating more complex patterns
including trends). The `auto.arima` function chooses whether to include each of
these components (and how many terms to include for each one) using AICc
[@forecast1]. Since there is no seasonal component to the BBS time-series, we
did not include a season component in these models. Otherwise we used the
default settings for this function [@forecast1].

>>>>

![**A.** Model predictions for Pennsylvania route 35 when all observers are
treated the same (black points). **B.** Model predictions for the same route
when accounting for systematic differences between observers (represented by the
points' colors). In this example most models are made more robust to observer 
turnover by including an observer model. Note that the "naive" model is less 
sensitive to observer turnover, and does not benefit as much from modeling
it.](../figures/observer_predictions.png)

@@

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in the package `forecast`; @forecast1] to represent an array of
different time-series modeling approaches. These models can include an
autoregressive component (as in the "naive" model, but with the possibility of
longer-term dependencies in the underlying process), a moving average component
(where the noise can have serial autocorrelation) and an
integration/differencing component (so that the analysis could be performed on
sequential differences of the raw data, accommodating more complex patterns
including trends). The `auto.arima` function chooses whether to include each of
these components (and how many terms to include for each one) using AICc
[@forecast1]. Since there is no seasonal component to the BBS time-series, we
did not include a season component in these models. Otherwise we used the
default settings for this function (See suppliment for details).
